### 2018-07-03 Thesis/Parts/Abstract/Abstract.tex
new thesis version

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality and application of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused on generic texts, which are not limited to the characteristics of in-domain texts such as rare domain-specific words or have been focussed on small sets of academic texts. This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.\\
\vspace*{\fill}
\\
We aim to have this thesis published in the proceedings of the 14th Asia Information Retrieval Societies (AIRS) Conference (\url{http://airs2018.org/site/page.aspx?pid=901&sid=1221&lang=en}). \textit{Paper submission deadline: 23 July 2018; Notification of acceptance: 27 August 2018}
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality and application of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused on generic texts, which are not limited to the characteristics of in-domain texts such as rare domain-specific words or have been focussed on small sets of academic texts. This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.\\
\vspace*{\fill}
\\
We aim to have this thesis published in the proceedings of the --- \textit{Paper submission deadline: xx XXXX 2018; Notification of acceptance: xx XXXX 2018}
\end{document}

### 2018-07-03 Thesis/Parts/Background/Background.tex
new thesis version

\subheader{Text analysis techniques}
To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm. In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
\begin{jumpin}
\subsubheader{Word2Vec}
Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window. Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}. There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW). The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}. This is illustrated in Figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words. \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach. Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
\begin{center}
\begin{figure}[hbt]
\includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}. Left part of the Figure illustrates the CBOW model, context words are represented at the left side (input) and the center word (output) is represented as $v(w)$ as output. The right side of the Figure illustrates the Skip-Gram Model, which takes the center word as input (left) and outputs the context words (right).}\label{figure:word2vecModels}
\end{figure}
\FloatBarrier
\end{center}
\subsubheader{Paragraph vectors}
Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector in their paper "Distributed representations of sentences and documents". The Paragraph Vector framework is based on the word vectors framework. The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses a matrix, which consists of every paragraph. This matrix is used to replace a concatenation or average of word vectors. An advantage of the paragraph vector model is that it takes the word order into consideration, at least in a small context \cite{le2014distributed}. \citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipedia and arXiv texts.

>>>>

\subheader{Text analysis techniques}
To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm. In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
\begin{jumpin}
\subsubheader{Word2Vec}
Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window. Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}. There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW). The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}. This is illustrated in Figure~\ref{figure:word2vecModels}, in this Figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words. \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach. Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
\begin{center}
\begin{figure}[hbt]
\includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}. Left part of the Figure illustrates the CBOW model, context words are represented at the left side (input) and the center word (output) is represented as $v(w)$ as output. The right side of the Figure illustrates the Skip-Gram Model, which takes the center word as input (left) and outputs the context words (right).}\label{figure:word2vecModels}
\end{figure}
\FloatBarrier
\end{center}
\subsubheader{Paragraph vectors}
Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector in their paper "Distributed representations of sentences and documents". The Paragraph Vector framework is based on the word vectors framework. The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses a matrix, which consists of every paragraph. This matrix is used to replace a concatenation or average of word vectors. An advantage of the paragraph vector model is that it takes the word order into consideration, at least in a small context \cite{le2014distributed}. \citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipedia and arXiv texts.

### 2018-07-03 Thesis/Parts/Data/Data.tex
new thesis version

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Corpus}
The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals. Details about the corpus can be found in table~\ref{table:corpusSize}.
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
 & Total count & Unique count & Average length \\
\hline\hline
Title words & $18.822.399$ & $939.665$ & 13,53  \\
\hline
Title tokens & $14.742.192$ & $230.805$ & 10,64 \\
\hline\hline
Abstract words & $264.653.020$ & $5.853.077$  & 190,19  \\
\hline
Abstract tokens & $171.474.473$ & $738.961$ & 123,71 \\
\hline\hline
Total words & $283.475.419$ & $6.209.769$  & 203,71 \\
\hline
Total tokens & $186.962.354$ & $763.475$ & 134,36 \\
\hline
\end{tabular}
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\end{table}
\clearpage
\subheader{Text properties}
\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language. Their models show that, due to the additional parameters in the Pareto-III, the tail of the data fits better with the model than the Zipf model. This shows the relation between the word occurrences rank and the actual occurrences. This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.
The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}. Our distribution is visualized in figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
\FloatBarrier
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/word_occurrences}
\caption{Word and token occurrences}\label{figure:wordTokenOccurrence}
\end{figure}
\FloatBarrier
\header{Datasets}
For this researched we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}). From this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\begin{enumerate}
\item{Removed punctuation}
\item{Removed all non-ASCII characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK\footnote{Natural Language ToolKit, \url{https://www.nltk.org/}} library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
\end{enumerate}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.

\subheader{Embedding}

@@

\subsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the figures as "embedding".
\subsubheader{TF-IDF weighted embedding}

@@

The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word. We will refer to this embedding in the figures as "tfidf\_embedding".
\subsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance. We will refer to this embedding in the figures as the "10k\_embedding".
\subsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise. We will refer to this embedding in the figures as "5k\_embedding".
\subsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set. We will refer to this embedding in the figures as "1k\_6k\_embedding". We refer to the "10k\_embedding", "5k\_embedding" and the "1k\_6k\_embedding" as the limited TF-IDF embeddings, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.

@@

\subheader{TF-IDF}

@@

We label the TF-IDF configurations as follows: $vocabulary size/hash bucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation. This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K". We will refer to the TF-IDF configurations in our figures as "tfidf\_vocabulary size\_hash bucket size".

@@

\caption{TF-IDF performance on title and abstract}\label{figure:tfidfMemory}

@@

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research Data}
\subheader{Corpus}
The dataset we used for this research consists of articles published in 2017 which have been published in a journal that has, in 2017, atleast 150 publications. This results in a total dataset of $1.391.543$ articles from $3.759$ journals. Details about the corpus can be found in table~\ref{table:corpusSize}.
\begin{center}
\begin{tabular}{|l|c|c|c|}
 & Total count & Unique count & Average length \\
\hline\hline
Title words & $18.822.399$ & $939.665$ & 13,53  \\
Title tokens & $14.742.192$ & $230.805$ & 10,64 \\
\hline\hline
Abstract words & $264.653.020$ & $5.853.077$  & 190,19  \\
Abstract tokens & $171.474.473$ & $738.961$ & 123,71 \\
\hline\hline
Total words & $283.475.419$ & $6.209.769$  & 203,71 \\
Total tokens & $186.962.354$ & $763.475$ & 134,36 \\
\end{center}
\caption{Corpus size}\label{table:corpusSize}
\subsubheader{Text properties}
\citet{wiegand2018word} state that the Pareto distribution offers a good fit to the word occurrences in natural language. Their models show that, due to the additional parameters in the Pareto-III\footnote{The pareto distribution is a distribution in which recognizable by a long "tail" of low values and a quick and short ascend to the top values. More information: \url{https://en.wikipedia.org/wiki/Pareto_distribution}.}, the tail of the data fits better with the model than the Zipf\footnote{Distribution similar to the Pareto distribution, see: \url{https://en.wikipedia.org/wiki/Zipf\%27s_law}} model. This shows the relation between the word occurrences rank and the actual occurrences. This kind of word-occurrences distribution holds for many texts, including the writings of William Shakespeare and scientific texts and novels\cite{thurner2015understanding}.
The word occurrences in our corpus also follow the pattern of a Pareto distribution as described by~\citet{wiegand2018word}. Our distribution is visualized in Figure~\ref{figure:wordTokenOccurrence}, which displays the occurrences of the first 500 tokens of the corpus.
\includegraphics[width=6.5in]{Plots/word_occurrences}
\caption{Word and token occurrences. The word counts pattern resembles a Pareto distribution, the tokenization reduced the amount of high frequency words.}\label{figure:wordTokenOccurrence}
\subheader{Datasets}
For this researched we used a (pre-made) tokenized dataset, created from the earlier described corpus, which reduces the total amount of words by 34\% (see table~\ref{table:corpusSize}). From this tokenized set, we created the embeddings and the TF-IDF feature vectors.
\subsubheader{Tokenization}
The following steps have been applied to the words to create a tokenized set:
\item{Removed punctuation}
\item{Removed all non-ASCII characters}
\item{Transformed all characters to lower-case}
\item{Removed stop-words, as provided by the NLTK\footnote{Natural Language ToolKit, \url{https://www.nltk.org/}} library}
\item{Removed numbers}
\item{Stemmed all words, using the stemmer provided by the NLTK library}
These transformations reduced our dataset by 34\%, resulting in a tokenized set of $186.962.354$ tokens.
\subsubheader{Embedding}

@@

\subsubsubheader{Default embedding}
The default embedding is created form the pre-trained word embeddings; no modifications have been applied to this set. We refer to this set in the Figures as \textbf{embedding}.
\subsubsubheader{TF-IDF weighted embedding}

@@

The articles embeddings are a normalized summation of each word vector multiplied by it TF-IDF value. Since we take a sum of all words, the Term Frequency is embedded as the raw count of each word. We will refer to this embedding in the Figures as \textbf{tfidf\_embedding}.
\subsubsubheader{10K TF-IDF embedding}
The 10K embedding set is generated similarity to the TF-IDF embedding, this version only uses the 10.000 most common tokens, reducing the number of tokens it uses. This set was created to see if the limitation to 10.000 tokens reduces the amount of noise, increasing the performance. We will refer to this embedding in the Figures as the \textbf{10k\_embedding}.
\subsubsubheader{5K TF-IDF embedding}
The 5K TF-IDF embedding is the TF-IDF embedding set, limited to the 5.000 most common words. This set was created to limit the number of tokens more aggressively, and with that, cancel out more noise. We will refer to this embedding in the Figures as \textbf{5k\_embedding}.
\subsubsubheader{1K-6K TF-IDF embedding}
The 1K-6K TF-IDF embedding is the TF-IDF embedding limited to the top 6.000 most common words, without the top 1.000 most common words. The rationale for this is that common words will occur in many articles, creating noise, by cutting off the top 1.000 and cutting off everything below 6.000 we tried to reduce the noise by filtering common words. This cut results in a set of 5.000 tokens, which allows us to compare it to the 5K TF-IDF set. We will refer to this embedding in the Figures as \textbf{1k\_6k\_embedding}. We refer to the \textbf{10k\_embedding}, \textbf{5k\_embedding} and the \textbf{1k\_6k\_embedding} as the \textbf{limited TF-IDF embeddings}, because these embedding use TF-IDF weighing, and have been limited in their vocabulary due to the cut-off's.

@@

\subsubheader{TF-IDF}

@@

We label the TF-IDF configurations as follows: $vocabulary size/hash bucket size$. Furthermore, we denote 1.000 as 1K, since we deal with chosen values which can be exactly noted given this notation. This means that the set with a 10.000 vocabulary size and a 10.000 hash bucket size will be denoted as "10K/10K". We will refer to the TF-IDF configurations in our Figures as "tfidf\_vocabulary size\_hash bucket size".

@@

\caption{TF-IDF memory usage for title and abstract combined}\label{figure:tfidfMemory}

@@

Figure~\ref{figure:tfidfPerformance} shows the performance of title and abstract as median rank, and Figure~\ref{figure:tfidfMemory} shows the storage size in gigabyte, of the 1k/1K, 4K/4K, 7K/7K and 10K/10K TF-IDF configurations. This plot shows that, while the required storage size stagnate, the performance on title also quickly stagnates, together with the performance on the abstracts. Given this information, we have chosen to use the 10K/10K, 10K/5K and 5K/5K configurations to compare our embedding results to. Since these configurations can be kept in memory (storage size) while it is not likely that larger sets will give much improvement. The TF-IDF features are created on article level. We average the set of article feature vectors to create a journal feature vector, just as we did with the embeddings. 

### 2018-07-03 Thesis/Parts/Discussion/Discussion.tex
new thesis version

\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}). This means that the titles contain less information than the abstracts. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
\clearpage
\subsubheader{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance. 
\begin{jumpin}
\subsubsubheader{Rank distribution}
However, Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.
\end{jumpin}This seems to indicate that the cut-off was effective, but that it did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings. Resulting in high median and average ranks, and in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However, they can be processed more efficiently during calculations}. This results in a lower memory requirement.

@@

\subsubheader{Journal plots}
Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector. In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together. 
The interactive version shows that the clusterings, as seen on all four figures, are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates. Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles. The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data. They have therefore a more reliable grouping metric.

>>>>

\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}). This means that the titles contain less information than the abstracts. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
\clearpage
\subsubheader{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance. 
\begin{jumpin}
\subsubsubheader{Rank distribution}
However, Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\vspace{0.3in}
\end{jumpin}
The rank distribution seems to indicate that the cut-off was effective, but also that it did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings. Resulting in high median and average ranks, and in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However, they can be processed more efficiently during calculations}. This results in a lower memory requirement.

@@

\subsubheader{Journal plots}
Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this Figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector. In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together. 
The interactive version shows that the clusterings, as seen on all four Figures, are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates. Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles. The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data. They have therefore a more reliable grouping metric.
